A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex

\subsubsection{Wearables Scenarios}
We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}

We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions:

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r |}
Rank & Data &  VUR  \\
\hline
1 & a video of you unclothed & 95.97\% \\
2 & bank account information & 95.91\% \\
3 & social security number & 94.84\% \\
4 & video of you entering in your PIN & 92.67\% \\
5 & a photo of you unclothed & 92.59\% \\
6 & an incriminating/embarrassing photo of you & 91.39\% \\
7 & username and password for websites & 89.55\% \\
8 & credit card information & 88.98\% \\
9 & an incriminating/embarrassing video of you & 88.41\% \\
10 & a random (inward-facing) photo you at home & 87.50\% \\
 & \vdots & \\
64 & eye movement patterns (for eye tracking) & 40.51\% \\
65 & when and how much you exercise  & 38.66\% \\
66 & when you are happy or having fun  & 34.51\% \\
67 & which television shows you watch & 30.20\% \\
68 & when you are busy or interruptible  & 29.50\% \\
69 & music from your device  & 28.06\% \\
70 & your heart rate & 27.50\% \\
71 & your age & 24.29\% \\
72 & the language you speak & 15.86\% \\
73 & your gender & 14.91\% \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 70.23\% VUR when asked about wearables devices and 40.62\% VUR when asked about smartphones.The VUR rates for both devices for all 5 quesions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
 Question &  Wearable VUR & Smartphone VUR \\
 \hline
 All & 70.23\% & 40.62\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.79\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\hline
\end{tabular}
\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{| c | c | c | c |}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\

%SE: Can you add sample sizes to this table?
Question & $\chi^2$ & p-value & $\phi$ \\
\hline
All & 2.814 & 0.1395 & 0.001\\
Q1 & 2.500 & 0.1139 & 0.004\\
Q2 & 17.333 & <0.0001 & 0.024\\
Q3 & 0.020 & 0.8886 & 0.000\\
Q4 & 1.426 & 0.2324 & 0.002\\
Q5 & 1.611 & 0.2043 & 0.002\\
\hline
\end{tabular}
\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
\label{betweendevice}
\end{center}
\end{table}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lll}

Concern &  Responses &  Frequency   \\
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\

\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}

@@

>>>>

\subsubsection{Wearables Scenarios}
We presented participants with scenarios involving data capture using the Cubetastic3000 and asked them to rate how upset they would be if a particular data type (e.g., video, audio, gestures, etc.) were shared with a particular data recipient without asking them first. All responses were collected on a 5-point Likert scale (from ``indifferent'' to ``very upset''), which was modeled after Felt et al.'s study of smartphone users' risk perceptions~\cite{Felt}. Questions were of the format, \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}. We created an initial pool of 288 questions by combining 72 data types (<data>) with 4 data recipients (<recipient>). The 4 possible data recipients were:  \\[-.8cm]

@@

\subsubsection{Smartphone Scenarios}

\label{sec:smartphones}

We presented participants with a second set of scenarios in order to control for the type of device being used. These questions followed the format of the previous question set, but substituted ``smartphone'' for ``Cubetastic3000.'' Rather than using the previous pool of 304 <data> and <recipient> combinations, we created 5 questions based on the scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented participants with 2 of the following 5 questions: \\[-.8cm]

@@

\begin{table}[t]
\begin{center}
\small
\begin{tabular}{| r | l | r |}
Rank & Data &  VUR  \\
\hline
1 & a video of you unclothed & 95.97\% \\
2 & bank account information & 95.91\% \\
3 & social security number & 94.84\% \\
4 & video of you entering in your PIN & 92.67\% \\
5 & a photo of you unclothed & 92.59\% \\
6 & an incriminating/embarrassing photo of you & 91.39\% \\
7 & username and password for websites & 89.55\% \\
8 & credit card information & 88.98\% \\
9 & an incriminating/embarrassing video of you & 88.41\% \\
10 & a random (inward-facing) photo you at home & 87.50\% \\
 & \vdots & \\
64 & eye movement patterns (for eye tracking) & 40.51\% \\
65 & when and how much you exercise  & 38.66\% \\
66 & when you are happy or having fun  & 34.75\% \\
67 & which television shows you watch & 30.20\% \\
68 & when you are busy or interruptible  & 29.50\% \\
69 & music from your device  & 28.06\% \\
70 & your heart rate & 27.50\% \\
71 & your age & 24.29\% \\
72 & the language you speak & 15.86\% \\
73 & your gender & 15.00\% \\ 
\hline
\end{tabular}
\caption{The 10 most and least upsetting data types, across all recipients.}
\label{top10}
\end{center}
\end{table}

@@

\subsubsection{Device Type}
Participants had unique VUR rates for situations only differing in the device. Our participants had a 58.79\% VUR when asked about wearables devices and 46.64\% VUR when asked about smartphones.The VUR rates for both devices for all 5 questions are in table ~\ref{deviceVUR}. However, the effect the device has on the VUR is not considered to be statistically significant (see Table ~\ref{betweendevice}). Additionally, there is no statistically significant difference between how people reacted in a given situation; although, participants were statistically significantly upset in Q2.  The aforementioned results are only with respect to between subjects analysis, where answers are from participants who received either only the wearables or smartphone version of the 5 questions. There were too few instances where a participant got both versions of questions (34 in total for all 5 questions), to be able to perform a within-subjects analysis.

\begin{table}[t]
\begin{center}
\begin{tabular}{| c | r | r |}
\hline
 Question &  Wearable VUR & Smartphone VUR \\
 \hline
 All & 58.79\% & 46.64\%\\
Q1 & 14.81\%  &  6.13\%\\
Q2 & 44.11\%  &  19.85\%\\
Q3 & 87.09\%  &  58.44\%\\
Q4 & 52.77\%  & 55.74\%\\
Q5 & 86.49\%  &  91.82\%\\ 
\hline
\end{tabular}
\caption{VURs for the questions described in Section \ref{sec:smartphones}, contrasting smartphones with the Cubetastic3000.}
\label{deviceVUR}
\end{center}
\end{table}

\begin{table}%[h]
\begin{center}
\begin{tabular}{|l|r|r|r|r|}
%Question & Chi^2 &	2-tail P &	Sig?	 & n	& effect size\\
%All	2.814	0.1395	No		3589		0.001\\
%Q1	2.500	0.1139	No		714		0.004\\
%Q2	17.333	<0.0001	Yes		708		0.024\\
%Q3	0.020	0.8886	No		699		0.000\\
%Q4	1.426	0.2324	No		731		0.002\\
%Q5	1.611		0.2043	No		710		0.002\\

%SE: Can you add sample sizes to this table?
Question & $\chi^2$ & p-value & n & $\phi$ \\
\hline
All & 2.202 & <0.1378 & 3,588 & 0.001\\
Q1 & 2.500 & <0.1139 & 714 & 0.004\\
Q2 & 17.333 & <0.0001 & 708 &  0.024\\
Q3 & 0.020 & <0.8886 & 699 &  0.000\\
Q4 & 1.413 & <0.2345 & 730& 0.002\\
Q5 & 1.604 & <0.2054 & 709 & 0.002\\
\hline
\end{tabular}
\caption{Chi-square test results comparing participants' VURs between the smartphone and Cubetastic3000 questions.}
\label{betweendevice}
\end{center}
\end{table}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\ \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Social Impact &	157 & 8.80\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{open-responses}
\end{center}
\end{table}

@@

\section{List of all <data>}
{\color{red} Placeholder for space measuring.} \\[-.8cm]

\begin{enumerate}\itemsep0pt \parskip0pt \parsep0pt
  \item foo
  \item bar
   \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
  \item foo
  \item bar
\end{enumerate}
